\bf Excuse me, do you have a moment to talk about version control?

### 2017-08-28 README.Rmd
Cite "Infrastructure and tools for teaching computing throughout the statistical curriculum"; closes #15
cc @mine-cetinkaya-rundel @rundel

  * Doing your work becomes tightly integrated with organizing, recording, and disseminating it. It's not a separate, burdensome task you are tempted to neglect.
  * Collaboration is much more structured, with powerful tools for asynchronous work and managing versions.
  * The marginal effort required to create a web presence for a project is negligible.
  * GitHub makes a fantastic course management system for courses that use R [@R]. You can exchange actual working code with your students and explore the associated results.
  * By using common mechanics across work modes (research, teaching, analysis), you achieve basic competence quickly and avoid the demoralizing forget-relearn cycle.

@@

Statistics is an important part of Data Science, though there is lively debate about the exact relationship, both past and future [@donoho]. I strongly disagree with glib claims that "Data Science is just Statistics", which can be heard in academia. For reasons both genuine and pragmatic, Statistics departments want to participate in the growth of Data Science at their respective universities. So far, their success has been decidedly mixed [@donoho]. In the era of Data Science, staying current can't be limited to mathematical and methodological developments. The holistic work style described here is widely regarded as current best practice, yet we generally neither practice nor preach it in academic statistics. It is but one example of the many ways in which Data Science is **not** just statistics. By acknowledging the importance of modern workflows and tooling, Statistics can solidify its claim to being one of the core disciplines of Data Science.

>>>>

  * Doing your work becomes tightly integrated with organizing, recording, and disseminating it. It's not a separate, burdensome task you are tempted to neglect.
  * Collaboration is much more structured, with powerful tools for asynchronous work and managing versions.
  * The marginal effort required to create a web presence for a project is negligible.
  * GitHub makes a fantastic course management system for courses that use R [@R]. You can exchange actual working code with your students and explore the associated results [@cetinkaya-rundel-dss-2017].
  * By using common mechanics across work modes (research, teaching, analysis), you achieve basic competence quickly and avoid the demoralizing forget-relearn cycle.

@@

Statistics is an important part of Data Science, though there is lively debate about the exact relationship, both past and future [@donoho]. I strongly disagree with glib claims that "Data Science is just Statistics", which can be heard in academia. For reasons both genuine and pragmatic, Statistics departments want to participate in the growth of Data Science at their respective universities. So far, their success has been decidedly mixed [@donoho]. In the era of Data Science, staying current can't be limited to mathematical and methodological developments. The holistic work style described here is widely regarded as current best practice, yet we generally neither practice nor preach it in academic statistics (but see [@cetinkaya-rundel-dss-2017] for an exception to this rule). It is but one example of the many ways in which Data Science is **not** just statistics. By acknowledging the importance of modern workflows and tooling, Statistics can solidify its claim to being one of the core disciplines of Data Science.

### 2017-08-28 README.tex
Cite "Infrastructure and tools for teaching computing throughout the statistical curriculum"; closes #15
cc @mine-cetinkaya-rundel @rundel

\begin{itemize}
\tightlist
\item
  Doing your work becomes tightly integrated with organizing, recording,
  and disseminating it. It's not a separate, burdensome task you are
  tempted to neglect.
\item
  Collaboration is much more structured, with powerful tools for
  asynchronous work and managing versions.
\item
  The marginal effort required to create a web presence for a project is
  negligible.
\item
  GitHub makes a fantastic course management system for courses that use
  R \citep{R}. You can exchange actual working code with your students
  and explore the associated results.
\item
  By using common mechanics across work modes (research, teaching,
  analysis), you achieve basic competence quickly and avoid the
  demoralizing forget-relearn cycle.
\end{itemize}

@@

Statistics is an important part of Data Science, though there is lively
debate about the exact relationship, both past and future
\citep{donoho}. I strongly disagree with glib claims that ``Data Science
is just Statistics'', which can be heard in academia. For reasons both
genuine and pragmatic, Statistics departments want to participate in the
growth of Data Science at their respective universities. So far, their
success has been decidedly mixed \citep{donoho}. In the era of Data
Science, staying current can't be limited to mathematical and
methodological developments. The holistic work style described here is
widely regarded as current best practice, yet we generally neither
practice nor preach it in academic statistics. It is but one example of
the many ways in which Data Science is \textbf{not} just statistics. By
acknowledging the importance of modern workflows and tooling, Statistics
can solidify its claim to being one of the core disciplines of Data
Science.

>>>>

\begin{itemize}
\tightlist
\item
  Doing your work becomes tightly integrated with organizing, recording,
  and disseminating it. It's not a separate, burdensome task you are
  tempted to neglect.
\item
  Collaboration is much more structured, with powerful tools for
  asynchronous work and managing versions.
\item
  The marginal effort required to create a web presence for a project is
  negligible.
\item
  GitHub makes a fantastic course management system for courses that use
  R \citep{R}. You can exchange actual working code with your students
  and explore the associated results \citep{cetinkaya-rundel-dss-2017}.
\item
  By using common mechanics across work modes (research, teaching,
  analysis), you achieve basic competence quickly and avoid the
  demoralizing forget-relearn cycle.
\end{itemize}

@@

Statistics is an important part of Data Science, though there is lively
debate about the exact relationship, both past and future
\citep{donoho}. I strongly disagree with glib claims that ``Data Science
is just Statistics'', which can be heard in academia. For reasons both
genuine and pragmatic, Statistics departments want to participate in the
growth of Data Science at their respective universities. So far, their
success has been decidedly mixed \citep{donoho}. In the era of Data
Science, staying current can't be limited to mathematical and
methodological developments. The holistic work style described here is
widely regarded as current best practice, yet we generally neither
practice nor preach it in academic statistics (but see
\citep{cetinkaya-rundel-dss-2017} for an exception to this rule). It is
but one example of the many ways in which Data Science is \textbf{not}
just statistics. By acknowledging the importance of modern workflows and
tooling, Statistics can solidify its claim to being one of the core
disciplines of Data Science.
